### 2009-01-06 articles/2009/geoinformatics/article.tex
added some text from VisualChangelog1.0
git-svn-id: https://svn.osgeo.org/qgis/trunk@9931 c8812cc2-4d05-0410-92ff-de0c093fc19c

\section{Quantum GIS 1.0.0}
\pagenumbering{arabic}
\setcounter{page}{1}

Quantum GIS (QGIS) is a cross-platform (GNU/Linux, MS Windows, Mac OSX) open
source application with a growing number of common GIS features and
functions. QGIS is licensed under the GNU General Public License and an
official member project of the Open Source Geospatial Foundation (OSGeo). The
current official version is 1.0.0, aka "Kore" and was released on January 05,
2009.

\subsection{History}

The idea for Quantum GIS was born in the beginning of 2002 when Gary Sherman
began looking for a GIS viewer for Linux that was fast and supported a wide
range of data stores. That, coupled with an interest in coding a GIS
application led to the creation of the project. In the beginning Quantum GIS
was established as a project on SourceForge in June 2002 with the first,
mostly non-functioning release on July 19, 2002. This first release supported
only PostGIS layers.

Within the last 7 years, the project

>>>>

\section{Quantum GIS 1.0}
\pagenumbering{arabic}
\setcounter{page}{1}

Quantum GIS (QGIS) is a user friendly Open Source Geographic Information
System (GIS), licensed under the GNU General Public License, that runs on
GNU/Linux, Unix, Mac OSX, and MS Windows. QGIS supports numerous vector, 
raster, and database formats and provides a wide variety of plugins to do 
things like display tracks from your GPS, edit and analyse vector geometries 
and attribute data, compose print layouts, and much more.

\subsection{History and Facts}

QGIS began life in February of 2002, with the first release in June of the
same year. The initial goal was to create a viewer for PostGIS data that ran
on Linux. From those humble beginnings, QGIS has become a true cross-platform
application that runs on all major versions of unix, Linux, as well as Mac
and Windows. It supports editing and map composition as well as integration
with GRASS to provide powerful GIS capability.

QGIS 1.0, released in January 2009 provides a stable API from which you can
develop custom solutions in Python or C++. Even though 1.0 is fresh, there
are a number of exciting developments underway in both the core application
and plugins.
